%
% This file was generated from the LISP module `lisp-doc' by extracting
% the LISP documentation strings of the files
%
%   ./lisp-doc.lisp
%
% as of 1997/09/18 8:09    (year/mm/dd hh:mm)
% Changes done here will be lost.
%
% lisp-doc (C) 1994,1997
%              Heiko Kirschke, Computer Science Dept., University of Hamburg
%
\let\tempa\relax%
\ifx\flabel\undefined%
 \let\tempa\endinput%
 Missing document substyle {\tt `crossref.sty'}; ending input.
 \message{^^J^^JMissing document substyle `crossref.sty'; ending input.^^J^^J}%
\fi%
\ifx\Seealsolabel\undefined%
 \let\tempa\endinput%
 Missing document substyle {\tt `lispdoc.sty'}; ending input.
 \message{^^J^^JMissing document substyle `lispdoc.sty'; ending input.^^J^^J}%
\fi%
\tempa\def\tempa{}%

\begindccom[Class Hierarchy]{CLOS Class Hierarchy}

\begingroup\def\fcitepage#1{#1}%
\hspace*{0\bigskipamount}%
{\bf lisp-comment}\dotfill{\rm\small[{\em Internal CLOS Class}\/]}%
\hbox to 1.55em{\hfil\rm\small \fpageref{lisp-comment}}%
\endgroup\\
\begingroup\def\fcitepage#1{#1}%
\hspace*{1\bigskipamount}%
{\bf comment-class}\dotfill{\rm\small[{\em Internal CLOS Class}\/]}%
\hbox to 1.55em{\hfil\rm\small \fpageref{comment-class}}%
\endgroup\\
\begingroup\def\fcitepage#1{#1}%
\hspace*{1\bigskipamount}%
{\bf comment-constant}\dotfill{\rm\small[{\em Internal CLOS Class}\/]}%
\hbox to 1.55em{\hfil\rm\small \fpageref{comment-constant}}%
\endgroup\\
\begingroup\def\fcitepage#1{#1}%
\hspace*{1\bigskipamount}%
{\bf comment-documentation}\dotfill{\rm\small[{\em Internal CLOS Class}\/]}%
\hbox to 1.55em{\hfil\rm\small \fpageref{comment-documentation}}%
\endgroup\\
\begingroup\def\fcitepage#1{#1}%
\hspace*{1\bigskipamount}%
{\bf comment-function}\dotfill{\rm\small[{\em Internal CLOS Class}\/]}%
\hbox to 1.55em{\hfil\rm\small \fpageref{comment-function}}%
\endgroup\\
\begingroup\def\fcitepage#1{#1}%
\hspace*{1\bigskipamount}%
{\bf comment-generic-function}\dotfill{\rm\small[{\em Internal CLOS Class}\/]}%
\hbox to 1.55em{\hfil\rm\small \fpageref{comment-generic-function}}%
\endgroup\\
\begingroup\def\fcitepage#1{#1}%
\hspace*{1\bigskipamount}%
{\bf comment-macro}\dotfill{\rm\small[{\em Internal CLOS Class}\/]}%
\hbox to 1.55em{\hfil\rm\small \fpageref{comment-macro}}%
\endgroup\\
\begingroup\def\fcitepage#1{#1}%
\hspace*{1\bigskipamount}%
{\bf comment-method}\dotfill{\rm\small[{\em Internal CLOS Class}\/]}%
\hbox to 1.55em{\hfil\rm\small \fpageref{comment-method}}%
\endgroup\\
\begingroup\def\fcitepage#1{#1}%
\hspace*{1\bigskipamount}%
{\bf comment-parameter}\dotfill{\rm\small[{\em Internal CLOS Class}\/]}%
\hbox to 1.55em{\hfil\rm\small \fpageref{comment-parameter}}%
\endgroup\\
\begingroup\def\fcitepage#1{#1}%
\hspace*{1\bigskipamount}%
{\bf comment-slot}\dotfill{\rm\small[{\em Internal CLOS Class}\/]}%
\hbox to 1.55em{\hfil\rm\small \fpageref{comment-slot}}%
\endgroup\\
\begingroup\def\fcitepage#1{#1}%
\hspace*{1\bigskipamount}%
{\bf comment-variable}\dotfill{\rm\small[{\em Internal CLOS Class}\/]}%
\hbox to 1.55em{\hfil\rm\small \fpageref{comment-variable}}%
\endgroup\\



\endcom

\beginvrcom[Internal]{*all-clos-classes*}

\Initialvaluelabel
\begin{verbatim}
nil
\end{verbatim}

\Purposelabel
A list containing all scanned \clos\ classes.


\endcom

\beginvrcom[Internal]{*all-structure-classes*}

\Initialvaluelabel
\begin{verbatim}
nil
\end{verbatim}

\Purposelabel
A list containing all scanned structure classes.


\endcom

\beginclcom[Internal]{comment-class}

\Purposelabel
 A class for documenting classes.
\Seealsolabel
 \Fcite{lisp-comment}.


\Directsuperclasseslabel
\Defmethod{}{\tt}{(lisp-comment\IfFLabelExists{lisp-comment}{{\rm\ \fpageref{lisp-comment}}}{})}{}


\Directslotslabel

\Defdslot {com-midfix} {:initarg :midfix\newline :initform +default-class-midfix+\newline :accessor comment-midfix}

\Defdslot {superclasses-label} {:initarg :superclasses-label\newline :initform +default-superclasses-label+\newline :accessor comment-superclasses-label}

Contains the \TeX\ label to use for slot
 {\bf superclasses}.

\Defdslot {superclasses} {:initarg :superclasses\newline :initform nil\newline :accessor comment-superclasses}

Contains a list of the direct superclasses of
 the documented class.

\Defdslot {metaclass-label} {:initarg :metaclass-label\newline :initform +default-metaclass-label+\newline :accessor comment-metaclass-label}

Contains the \TeX\ label to use for slot
 {\bf metaclass}.

\Defdslot {metaclass} {:initarg :metaclass\newline :initform nil\newline :accessor comment-metaclass}

Contains the metaclass of the documented class.

\Defdslot {slots-label} {:initarg :slots-label\newline :initform +default-slots-label+\newline :accessor comment-slots-label}

Contains the \TeX\ label to use for slot
 {\bf slots}.

\Defdslot {slots} {:initarg :slots\newline :initform nil\newline :accessor comment-slots}

Contains a list of the direct slots of
 the documented class.

\Defdslot {class-options-label} {:initarg :class-options-label\newline :initform +default-class-options-label+\newline :accessor comment-class-options-label}

Contains the \TeX\ label to use for slot
 {\bf class-options}.

\Defdslot {class-options} {:initarg :class-options\newline :initform nil\newline :accessor comment-class-options}

Contains the class options of the documented class.


\endcom

\message{^^JGeneric function comment-class-options has no methods.^^J}
\message{^^JGeneric function (setf comment-class-options) has no methods.^^J}
\message{^^JGeneric function comment-class-options-label has no methods.^^J}
\message{^^JGeneric function (setf comment-class-options-label) has no methods.^^J}
\beginclcom[Internal]{comment-constant}

\Purposelabel
 A class for documenting constants.
\Seealsolabel
 \Fcite{lisp-comment}.


\Directsuperclasseslabel
\Defmethod{}{\tt}{(lisp-comment\IfFLabelExists{lisp-comment}{{\rm\ \fpageref{lisp-comment}}}{})}{}


\Directslotslabel

\Defdslot {com-midfix} {:initarg :midfix\newline :initform +default-constant-midfix+\newline :accessor comment-midfix}


\endcom

\beginclcom[Internal]{comment-documentation}

\Purposelabel
 A class for documenting-only items.
\Seealsolabel
 \Fcite{lisp-comment}.


\Directsuperclasseslabel
\Defmethod{}{\tt}{(lisp-comment\IfFLabelExists{lisp-comment}{{\rm\ \fpageref{lisp-comment}}}{})}{}


\Directslotslabel

\Defdslot {com-midfix} {:initarg :midfix\newline :initform +default-documentation-midfix+\newline :accessor comment-midfix}


\endcom

\beginclcom[Internal]{comment-function}

\Purposelabel
 A class for documenting functions.
\Seealsolabel
 \Fcite{lisp-comment}.


\Directsuperclasseslabel
\Defmethod{}{\tt}{(lisp-comment\IfFLabelExists{lisp-comment}{{\rm\ \fpageref{lisp-comment}}}{})}{}


\Directslotslabel

\Defdslot {com-midfix} {:initarg :midfix\newline :initform +default-function-midfix+\newline :accessor comment-midfix}


\endcom

\beginclcom[Internal]{comment-generic-function}

\Purposelabel
 A class for documenting generic functions.
\Seealsolabel
 \Fcite{lisp-comment}.


\Directsuperclasseslabel
\Defmethod{}{\tt}{(lisp-comment\IfFLabelExists{lisp-comment}{{\rm\ \fpageref{lisp-comment}}}{})}{}


\Directslotslabel

\Defdslot {com-midfix} {:initarg :midfix\newline :initform +default-generic-function-midfix+\newline :accessor comment-midfix}

\Defdslot {methods-label} {:initarg :methods-label\newline :initform +default-methods-label+\newline :accessor comment-methods-label}

Contains the \TeX\ label to use for slot
 {\bf methods}.

\Defdslot {methods} {:initarg :methods\newline :initform nil\newline :accessor comment-methods}


 Contains a list of method documentations belonging to the
 generic function.


\endcom

\message{^^JGeneric function comment-key has no methods.^^J}
\message{^^JGeneric function (setf comment-key) has no methods.^^J}
\message{^^JGeneric function comment-key-attribute has no methods.^^J}
\message{^^JGeneric function (setf comment-key-attribute) has no methods.^^J}
\beginclcom[Internal]{comment-macro}

\Purposelabel
 A class for documenting macros.
\Seealsolabel
 \Fcite{lisp-comment}.


\Directsuperclasseslabel
\Defmethod{}{\tt}{(lisp-comment\IfFLabelExists{lisp-comment}{{\rm\ \fpageref{lisp-comment}}}{})}{}


\Directslotslabel

\Defdslot {com-midfix} {:initarg :midfix\newline :initform +default-macro-midfix+\newline :accessor comment-midfix}


\endcom

\message{^^JGeneric function comment-metaclass has no methods.^^J}
\message{^^JGeneric function (setf comment-metaclass) has no methods.^^J}
\message{^^JGeneric function comment-metaclass-label has no methods.^^J}
\message{^^JGeneric function (setf comment-metaclass-label) has no methods.^^J}
\beginclcom[Internal]{comment-method}

\Purposelabel
 A class for documenting methods.
\Seealsolabel
 \Fcite{lisp-comment}.


\Directsuperclasseslabel
\Defmethod{}{\tt}{(lisp-comment\IfFLabelExists{lisp-comment}{{\rm\ \fpageref{lisp-comment}}}{})}{}


\Directslotslabel

\Defdslot {metaobject} {:initarg :metaobject\newline :initform nil\newline :accessor method-metaobject}

The method metaobject of the documented method.

\Defdslot {qualifiers} {:initarg :qualifiers\newline :initform nil\newline :accessor method-qualifiers}

\Defdslot {specializers} {:initarg :specializers\newline :initform nil\newline :accessor method-specializers}

\Defdslot {syntax-label} {:initarg :syntax-label\newline :initform nil\newline :accessor comment-syntax-label}


 Since methods don't have a {\sc Syntax} label, this slot is always
 initialized to \lispnil.


\endcom

\message{^^JGeneric function comment-methods has no methods.^^J}
\message{^^JGeneric function (setf comment-methods) has no methods.^^J}
\message{^^JGeneric function comment-methods-label has no methods.^^J}
\message{^^JGeneric function (setf comment-methods-label) has no methods.^^J}
\message{^^JGeneric function comment-midfix has no methods.^^J}
\message{^^JGeneric function (setf comment-midfix) has no methods.^^J}
\beginclcom[Internal]{comment-parameter}

\Purposelabel
 A class for documenting parameters.
\Seealsolabel
 \Fcite{lisp-comment}.


\Directsuperclasseslabel
\Defmethod{}{\tt}{(lisp-comment\IfFLabelExists{lisp-comment}{{\rm\ \fpageref{lisp-comment}}}{})}{}


\Directslotslabel

\Defdslot {com-midfix} {:initarg :midfix\newline :initform +default-parameter-midfix+\newline :accessor comment-midfix}


\endcom

\beginclcom[Internal]{comment-slot}

\Purposelabel
 A class for documenting slots of classes.
\Seealsolabel
 \Fcite{lisp-comment}.


\Directsuperclasseslabel
\Defmethod{}{\tt}{(lisp-comment\IfFLabelExists{lisp-comment}{{\rm\ \fpageref{lisp-comment}}}{})}{}


\Directslotslabel

\Defdslot {metaobject} {:initarg :metaobject\newline :initform nil\newline :accessor method-metaobject}

The method metaobject of the documented slot.

\Defdslot {syntax-label} {:initarg :syntax-label\newline :initform nil\newline :accessor comment-syntax-label}


\endcom

\message{^^JGeneric function comment-slots has no methods.^^J}
\message{^^JGeneric function (setf comment-slots) has no methods.^^J}
\message{^^JGeneric function comment-slots-label has no methods.^^J}
\message{^^JGeneric function (setf comment-slots-label) has no methods.^^J}
\message{^^JGeneric function comment-superclasses has no methods.^^J}
\message{^^JGeneric function (setf comment-superclasses) has no methods.^^J}
\message{^^JGeneric function comment-superclasses-label has no methods.^^J}
\message{^^JGeneric function (setf comment-superclasses-label) has no methods.^^J}
\message{^^JGeneric function comment-syntax has no methods.^^J}
\message{^^JGeneric function (setf comment-syntax) has no methods.^^J}
\message{^^JGeneric function comment-syntax-label has no methods.^^J}
\message{^^JGeneric function (setf comment-syntax-label) has no methods.^^J}
\message{^^JGeneric function comment-text has no methods.^^J}
\message{^^JGeneric function (setf comment-text) has no methods.^^J}
\beginclcom[Internal]{comment-variable}

\Purposelabel
 A class for documenting variables.
\Seealsolabel
 \Fcite{lisp-comment}.


\Directsuperclasseslabel
\Defmethod{}{\tt}{(lisp-comment\IfFLabelExists{lisp-comment}{{\rm\ \fpageref{lisp-comment}}}{})}{}


\Directslotslabel

\Defdslot {com-midfix} {:initarg :midfix\newline :initform +default-variable-midfix+\newline :accessor comment-midfix}


\endcom

\begincncom[Internal]{+default-class-midfix+}

\Valuelabel
\begin{verbatim}
"cl"
\end{verbatim}

\Purposelabel
The text to put into the \verb|\begin..com| command for
 classes.


\endcom

\begincncom[Internal]{+default-class-options-label+}

\Valuelabel
\begin{verbatim}
"\\Classoptionslabel"
\end{verbatim}

\Purposelabel
The default \TeX\ command string for generating the
 {\sc Class Options} label.


\endcom

\begincncom[Internal]{+default-constant-midfix+}

\Valuelabel
\begin{verbatim}
"cn"
\end{verbatim}

\Purposelabel
The text to put into the \verb|\begin..com| command for
 constants.


\endcom

\begincncom[Internal]{+default-documentation-midfix+}

\Valuelabel
\begin{verbatim}
"dc"
\end{verbatim}

\Purposelabel
The text to put into the \verb|\begin..com| command for
 documented items.


\endcom

\begincncom[Internal]{+default-function-midfix+}

\Valuelabel
\begin{verbatim}
"fn"
\end{verbatim}

\Purposelabel
The text to put into the \verb|\begin..com| command for
 functions.


\endcom

\begincncom[Internal]{+default-generic-function-midfix+}

\Valuelabel
\begin{verbatim}
"gf"
\end{verbatim}

\Purposelabel
The text to put into the \verb|\begin..com| command for
 generic functions.


\endcom

\begincncom[Internal]{+default-macro-midfix+}

\Valuelabel
\begin{verbatim}
"mc"
\end{verbatim}

\Purposelabel
The text to put into the \verb|\begin..com| command for
 macros.


\endcom

\begincncom[Internal]{+default-metaclass-label+}

\Valuelabel
\begin{verbatim}
"\\Metaclasslabel"
\end{verbatim}

\Purposelabel
The default \TeX\ command string for generating the
 {\sc Metaobject Class} label.


\endcom

\begincncom[Internal]{+default-method-text+}

\Valuelabel
\begin{verbatim}
"%
% No behavior is specified for this method beyond that which is specified
% for the generic function."
\end{verbatim}

\Purposelabel
The default text for methods without any documentation.


\endcom

\begincncom[Internal]{+default-methods-label+}

\Valuelabel
\begin{verbatim}
"\\Methodslabel"
\end{verbatim}

\Purposelabel
The default \TeX\ command string for generating the
 {\it Methods} label.


\endcom

\begincncom[Internal]{+default-parameter-midfix+}

\Valuelabel
\begin{verbatim}
"pm"
\end{verbatim}

\Purposelabel
The text to put into the \verb|\begin..com| command for
 parameters.


\endcom

\begincncom[Internal]{+default-slots-label+}

\Valuelabel
\begin{verbatim}
"\\Directslotslabel"
\end{verbatim}

\Purposelabel
The default \TeX\ command string for generating the
 {\sc Direct Slots} label.


\endcom

\begincncom[Internal]{+default-superclasses-label+}

\Valuelabel
\begin{verbatim}
"\\Directsuperclasseslabel"
\end{verbatim}

\Purposelabel
The default \TeX\ command string for generating the
 {\sc Direct Superclasses} label.


\endcom

\begincncom[Internal]{+default-syntax-label+}

\Valuelabel
\begin{verbatim}
"\\Syntaxlabel"
\end{verbatim}

\Purposelabel
The default \TeX\ command string for generating the
 {\sc Syntax} label.


\endcom

\begincncom[Internal]{+default-syntax-postfix+}

\Valuelabel
\begin{verbatim}
""
\end{verbatim}

\Purposelabel
The default postfix to append after a syntax text.


\endcom

\begincncom[Internal]{+default-variable-midfix+}

\Valuelabel
\begin{verbatim}
"vr"
\end{verbatim}

\Purposelabel
The text to put into the \verb|\begin..com| command for
 variables.


\endcom

\begincncom[Internal]{+exported-label+}

\Valuelabel
\begin{verbatim}
"External"
\end{verbatim}

\Purposelabel
The string used as {\it External} label in a document item header.


\endcom

\begindccom[Document Items with `free' Text]{free item ...}

This is a document item not bound to a programming construct:
\begin{lispcode}
#+lisp-doc
(:defdoc
 "free item ..."      ; This could be also a symbol
 "Document Items with `free' Text"
 "This is a document item not bound to a programming construct:
  ...")
\end{lispcode}

 It is only `seen' by the LISP reader when \lisp{:lisp-doc}\ is on the
 \lisp{*features*}\ list; this is accomplished by
 \lisp{lisp-doc}\ during scanning a LISP file.

 This item is sorted accroding to its first sort-key `parameter' behind
 the \lisp{:defdoc}\ statement.

 You can also use \verb|\fcite{}| on these items by using the sort key
 as argument, e.g.\ \verb|\fcite{free item ...}| gives
 `\fcite{free item ...}'.


\endcom

\beginvrcom[Internal]{*generic-function-name->comment*}

\Initialvaluelabel
\begin{verbatim}
(make-hash-table :test 'equal)
\end{verbatim}

\Purposelabel
A hash table mapping a generic function name to its
 documenting object.


\endcom

\beginfncom[Internal]{insert-class}

\Syntaxlabel
\Defun {insert-class} {\funarg{the-class} \linebreak[3]\ \funarg{class-list}}

Insert \funarg{the-class}\ into \funarg{class-list}.


\endcom

\begincncom[Internal]{+internal-label+}

\Valuelabel
\begin{verbatim}
"Internal"
\end{verbatim}

\Purposelabel
The string used as {\it Internal} label in a document item header.


\endcom

\beginclcom[Internal]{lisp-comment}

\Purposelabel
 A class for representing comments. For each documented item,
 an instance of {\bf lisp-comment} is created.


\Directslotslabel

\Defdslot {com-midfix} {:initarg :midfix\newline :initform nil\newline :accessor comment-midfix}


 The text to put into the \verb|\begin..com| command.

\Defdslot {key} {:initarg :key\newline :initform nil\newline :accessor comment-key}


 The Keyword of the comment.
 The documentation is sorted according to this keyword.

\Defdslot {key-attribute} {:initarg :key-attribute\newline :initform nil\newline :accessor comment-key-attribute}


 The text attribute for key; normally, this contains either the
 {\it Internal} or {\it Exported} label.

\Defdslot {syntax-label} {:initarg :syntax-label\newline :initform +default-syntax-label+\newline :accessor comment-syntax-label}


 The \TeX\ command string to generate the {\sc Syntax} label for
 the document item.

\Defdslot {syntax} {:initarg :syntax\newline :initform nil\newline :accessor comment-syntax}


 The syntax description for the documented item.

\Defdslot {text} {:initarg :text\newline :initform nil\newline :accessor comment-text}


 Contains a textual description of key. This is normally the literal
 read documentation string.


\endcom

\beginfncom[Internal]{make-class-options-comment}

\Syntaxlabel
\Defun {make-class-options-comment} {\funarg{class-options}}


\Argumentslabel

 \isa{\funarg{class-options}}
      {a list with class-option value pairs}
\Purposelabel
 Returns \funarg{class-options}\ transformed into a \TeX\ command
 sequence.


\endcom

\beginfncom[Internal]{make-function-comment}

\Syntaxlabel
\Defun {make-function-comment} {\funarg{function-name} \linebreak[3]\ \funarg{lambda-list}}


\Argumentslabel
 \isa{\funarg{function-name}}
      {a symbol}
 \isa{\funarg{lambda-list}}
      {a $\lambda$-list}
\Purposelabel
 Transform the function named by \funarg{function-name}\ with
 $\lambda$-list \funarg{lambda-list}\ into a \TeX\ command sequence.
\Seealsolabel
 \Fcite{make-lambda-list-comment}.


\endcom

\beginfncom[Internal]{make-key-attribute}

\Syntaxlabel
\Defun {make-key-attribute} {\funarg{name}}


\Purposelabel
 Check if \funarg{name}\ is an external name
 resp.\ to {\tt *package*}.
\Seealsolabel
 \Fcite{+internal-label+};
 \fcite{+exported-label+}.


\endcom

\beginfncom[Internal]{make-lambda-list-comment}

\Syntaxlabel
\Defun {make-lambda-list-comment} {\funarg{lambda-list}}


\Argumentslabel
 \isa{\funarg{lambda-list}}
      {a $\lambda$-list}
\Purposelabel
 Returns \funarg{lambda-list}\ transformed into a \TeX\ command
 sequence.


\endcom

\begingfcom[Internal]{make-lisp-comment}

\Syntaxlabel
\Defgen {make-lisp-comment} {\funarg{keyword} \linebreak[3]\ \funarg{expression}}


\Argumentslabel
 \isa{\funarg{keyword}}
      {a symbol}
 \isa{\funarg{expression}}
      {a list}
\Valueslabel
 Returns either \lispnil\ or an instance of [a subclass of]
 \fcite{lisp-comment}\ which contain comment items for
 \funarg {keyword}.
\Purposelabel
 Make a comment from \funarg{keyword}; \funarg{expression}\ contains
 the expression read from the source file.


\Methodslabel

\Defmeth {make-lisp-comment} {(\funarg{keyword}\ (eql 'defclass)\IfFLabelExists{(eql 'defclass)}{{\rm\ \fpageref{(eql 'defclass)}}}{}) \linebreak[3]\ \funarg{expression}}\flabel{\protect\mtd}{make-lisp-comment ((eql 'defclass) t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmeth {make-lisp-comment} {(\funarg{keyword}\ (eql 'defconstant)\IfFLabelExists{(eql 'defconstant)}{{\rm\ \fpageref{(eql 'defconstant)}}}{}) \linebreak[3]\ \funarg{expression}}\flabel{\protect\mtd}{make-lisp-comment ((eql 'defconstant) t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmeth {make-lisp-comment} {(\funarg{keyword}\ (eql 'defgeneric)\IfFLabelExists{(eql 'defgeneric)}{{\rm\ \fpageref{(eql 'defgeneric)}}}{}) \linebreak[3]\ \funarg{expression}}\flabel{\protect\mtd}{make-lisp-comment ((eql 'defgeneric) t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmeth {make-lisp-comment} {(\funarg{keyword}\ (eql 'defmacro)\IfFLabelExists{(eql 'defmacro)}{{\rm\ \fpageref{(eql 'defmacro)}}}{}) \linebreak[3]\ \funarg{expression}}\flabel{\protect\mtd}{make-lisp-comment ((eql 'defmacro) t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmeth {make-lisp-comment} {(\funarg{keyword}\ (eql 'defmethod)\IfFLabelExists{(eql 'defmethod)}{{\rm\ \fpageref{(eql 'defmethod)}}}{}) \linebreak[3]\ \funarg{expression}}\flabel{\protect\mtd}{make-lisp-comment ((eql 'defmethod) t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmeth {make-lisp-comment} {(\funarg{keyword}\ (eql 'defparameter)\IfFLabelExists{(eql 'defparameter)}{{\rm\ \fpageref{(eql 'defparameter)}}}{}) \linebreak[3]\ \funarg{expression}}\flabel{\protect\mtd}{make-lisp-comment ((eql 'defparameter) t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmeth {make-lisp-comment} {(\funarg{keyword}\ (eql 'defstruct)\IfFLabelExists{(eql 'defstruct)}{{\rm\ \fpageref{(eql 'defstruct)}}}{}) \linebreak[3]\ \funarg{expression}}\flabel{\protect\mtd}{make-lisp-comment ((eql 'defstruct) t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmeth {make-lisp-comment} {(\funarg{keyword}\ (eql 'defun)\IfFLabelExists{(eql 'defun)}{{\rm\ \fpageref{(eql 'defun)}}}{}) \linebreak[3]\ \funarg{expression}}\flabel{\protect\mtd}{make-lisp-comment ((eql 'defun) t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmeth {make-lisp-comment} {(\funarg{keyword}\ (eql 'defvar)\IfFLabelExists{(eql 'defvar)}{{\rm\ \fpageref{(eql 'defvar)}}}{}) \linebreak[3]\ \funarg{expression}}\flabel{\protect\mtd}{make-lisp-comment ((eql 'defvar) t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmeth {make-lisp-comment} {(\funarg{keyword}\ (eql :defdoc)\IfFLabelExists{(eql :defdoc)}{{\rm\ \fpageref{(eql :defdoc)}}}{}) \linebreak[3]\ \funarg{expression}}\flabel{\protect\mtd}{make-lisp-comment ((eql defdoc) t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmeth {make-lisp-comment} {\funarg{keyword} \linebreak[3]\ \funarg{expression}}\flabel{\protect\mtd}{make-lisp-comment (t t)}{}
Return always \lispnil; this will generate no document text at all.


\endcom

\beginfncom[Internal]{make-slot-comment}

\Syntaxlabel
\Defun {make-slot-comment} {\funarg{class-name} \linebreak[3]\ \funarg{expression} \linebreak[3]\ {\opt} \linebreak[3]\ \funarg{first-option}}


\Argumentslabel
 \isa{\funarg{expression}}
      {a slot-defining expression}
\Purposelabel
 Returns \funarg{expression}\ transformed into an instance of
 \fcite{comment-slot}.


\endcom

\beginfncom[Internal]{make-sort-key}

\Syntaxlabel
\Defun {make-sort-key} {\funarg{raw-key}}


\Argumentslabel
 \isa{\funarg{raw-key}}
      {either a symbol or a \lisp{setf}-expression}
\Purposelabel
 Transform \funarg{raw-key}\ into a string which is used for sorting
 the document items.
\Seealsolabel
 \Fcite{make-lambda-list-comment}.


\endcom

\message{^^JGeneric function method-metaobject has no methods.^^J}
\message{^^JGeneric function (setf method-metaobject) has no methods.^^J}
\message{^^JGeneric function method-qualifiers has no methods.^^J}
\message{^^JGeneric function (setf method-qualifiers) has no methods.^^J}
\message{^^JGeneric function method-specializers has no methods.^^J}
\message{^^JGeneric function (setf method-specializers) has no methods.^^J}
\begingfcom[External]{print-object}

\Syntaxlabel
\Defgen {print-object} {\funarg{instance} \linebreak[3]\ \funarg{stream}}


 See \fcite{print-object}.


\Methodslabel

\Defmeth {print-object} {(\funarg{object}\ lisp-comment\IfFLabelExists{lisp-comment}{{\rm\ \fpageref{lisp-comment}}}{}) \linebreak[3]\ \funarg{stream}}\flabel{\protect\mtd}{print-object (lisp-comment t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.


\endcom

\begincncom[Internal]{+qualifier-ordering+}

\Valuelabel
\begin{verbatim}
'(:around :before nil :after)
\end{verbatim}

\Purposelabel
A list imposing an ordering on method qualifiers for computing
   the order of methods to be printed.


\endcom

\beginfncom[Internal]{quote-tex-characters}

\Syntaxlabel
\Defun {quote-tex-characters} {\funarg{raw-string}}


\Argumentslabel
 \isa{\funarg{raw-string}}
      {a string with \TeX\ commands}
\Purposelabel
 Put a backslash before all \TeX\ special characters.


\endcom

\begincncom[Internal]{+reader-lambda-list+}

\Valuelabel
\begin{verbatim}
'(instance)
\end{verbatim}

\Purposelabel
The lambda list of a reader generic function.


\endcom

\beginfncom[External]{scan-file}

\Syntaxlabel
\Defun {scan-file} {{\rest} \linebreak[3]\ \funarg{all-args}}

See \fcite{scan-files}.


\endcom

\beginfncom[External]{scan-files}

\Syntaxlabel
\Defun {scan-files} {\funarg{file-list} \linebreak[3]\ {\opt} \linebreak[3]\ \funarg{to-stream}}


\Argumentslabel
 \isa{\funarg{file-list}}
      {a list with LISP source file names without
       \lisp{.lisp}\ extension}
 \isa{\funarg{to-stream}}
      {either \lispnil\ or a string or a \cl\ output stream}
\Valueslabel
 The output stream which was used for creating the \TeX\ file is
 returned.
\Purposelabel
 Scan the LISP source files in \funarg{file-list}\ and write their
 documentation to \funarg{to-stream}.


\endcom

\beginfncom[External]{scan-myself}

\Syntaxlabel
\Defun {scan-myself} {{\opt} \linebreak[3]\ \funarg{my-path}}


\Argumentslabel
 \isa{\funarg{my-path}}
      {a path expression}
\Purposelabel
 Extract the documentation strings from module \lisp{lisp-doc}.
 The \funarg{my-path}\ argument contains the path information
 where the \lisp{lisp-doc}\ file is located.
\Seealsolabel
 \Fcite{scan-files}.


\endcom

\beginfncom[Internal]{scan-one-file}

\Syntaxlabel
\Defun {scan-one-file} {\funarg{filename}}


\Argumentslabel
 \isa{\funarg{filename}}
      {a pathname}
\Purposelabel
 Scan file named by \funarg{filename}\ and extract its documentation.
\Seealsolabel
 \Fcite{scan-files}.


\endcom

\begingfcom[Internal]{ship-out}

\Syntaxlabel
\Defgen {ship-out} {\funarg{comment} \linebreak[3]\ \funarg{to-stream}}


\Argumentslabel
 \isa{\funarg{comment}}
      {an instance of [a subclass of] \fcite{lisp-comment}}
 \isa{\funarg{to-stream}}
      {a \cl\ output stream}
\Purposelabel
 Write \funarg{comment}\ as \TeX\ command sequence to
 \funarg{to-stream}.


\Methodslabel

\Defmetharound {ship-out} {(\funarg{c}\ comment-generic-function\IfFLabelExists{comment-generic-function}{{\rm\ \fpageref{comment-generic-function}}}{}) \linebreak[3]\ \funarg{to-stream}}\flabel{\protect\mtd}{ship-out :around (comment-generic-function t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmethb {ship-out} {\funarg{comment} \linebreak[3]\ \funarg{to-stream}}\flabel{\protect\mtd}{ship-out :before (t t)}{}
Write out the \verb|\begin..com| command.

\Defmeth {ship-out} {(\funarg{c}\ comment-class\IfFLabelExists{comment-class}{{\rm\ \fpageref{comment-class}}}{}) \linebreak[3]\ \funarg{to-stream}}\flabel{\protect\mtd}{ship-out (comment-class t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmeth {ship-out} {(\funarg{c}\ comment-generic-function\IfFLabelExists{comment-generic-function}{{\rm\ \fpageref{comment-generic-function}}}{}) \linebreak[3]\ \funarg{to-stream}}\flabel{\protect\mtd}{ship-out (comment-generic-function t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmeth {ship-out} {(\funarg{c}\ lisp-comment\IfFLabelExists{lisp-comment}{{\rm\ \fpageref{lisp-comment}}}{}) \linebreak[3]\ \funarg{to-stream}}\flabel{\protect\mtd}{ship-out (lisp-comment t)}{}
%
% No behavior is specified for this method beyond that which is specified
% for the generic function.

\Defmetha {ship-out} {\funarg{comment} \linebreak[3]\ \funarg{to-stream}}\flabel{\protect\mtd}{ship-out :after (t t)}{}
Write out the \verb|\endcom| command.


\endcom

\beginfncom[Internal]{ship-out-class-tree}

\Syntaxlabel
\Defun {ship-out-class-tree} {\funarg{class-list} \linebreak[3]\ \funarg{name} \linebreak[3]\ \funarg{to-stream}}

Write \funarg{class-list}\ as a class tree to \funarg{to-stream}.


\endcom

\beginfncom[Internal]{ship-out-label-and-argument}

\Syntaxlabel
\Defun {ship-out-label-and-argument} {\funarg{label} \linebreak[3]\ \funarg{argument} \linebreak[3]\ \funarg{to-stream}}


\Purposelabel
 Write \funarg{argument}\ as \TeX\ command sequence following
 the \funarg{label}\ to \funarg{to-stream}.
\Seealsolabel
 \Fcite{ship-out}.


\endcom

\begincncom[Internal]{+undocumented-item-prompt+}

\Valuelabel
\begin{verbatim}
";; *** Warning: Undocumented ~A ~S~%"
\end{verbatim}

\Purposelabel
Prompt for \lisp{undocumented ...}\ warnings.


\endcom

\begincncom[Internal]{+unknown-qualifier-continue-prompt+}

\Valuelabel
\begin{verbatim}
"Dont't order the methods."
\end{verbatim}

\Purposelabel
The continue prompt for unknown method qualifiers.


\endcom

\begincncom[Internal]{+unknown-qualifier-error-prompt+}

\Valuelabel
\begin{verbatim}
"Found unknown qualifier ~A in method ~A."
\end{verbatim}

\Purposelabel
The error prompt for unknown method qualifiers.


\endcom

\begincncom[Internal]{+writer-lambda-list+}

\Valuelabel
\begin{verbatim}
'(new-value instance)
\end{verbatim}

\Purposelabel
The lambda list of a writer generic function.


\endcom

