\chapter{Contributions and acknowledgements}

First of all, I would like to thank
\href{mailto:schroeder@acm.org}{Carsten Schr\"{o}der}\ for his advice and interesting discussions when starting my work on
\plob\ He provided me with the first ideas on object-oriented
persistency and assisted me in understanding LISP, CLOS and MOP.
Without these conversations, this system surely would not look like as
it does now.

I would like to thank the
\href{http://www-ppg.dcs.st-andrew.ac.uk/Default.html}{Persistent
  Programming Research Group} at St.\ Andrews University for the
permission to use and re-distribute their POSTORE library my server is
built upon.  The port to SGI's IRIX would not have been possible
without the help of \href{mailto:hunter@work.nlm.nih.gov}{Larry
  Hunter}.  The questions of
\href{mailto:jwchoi@lgsemicon.co.kr}{Jong-won Choi}\ have been a big
help at writing this user's guide.
\href{mailto:vfr750@netcom.com}{Will Hartung}\ reported the bug on
starting the \lisp{portmap}\ daemon.
\href{mailto:moeller@informatik.uni-hamburg.de}{Ralf M\"{o}ller}\ was
the first one who did a stress testing on \plob\ by using it in
conjunction with \lisp{cl-http}\ and storing a lot of real-world data.
The cooperation with him fixed many bugs and gave me some hints on how
\plob\ could be improved.  \href{mailto:mha@dpe.fi}{Martti Halminen}\ 
contributed to this user's guide by doing the first proof reading.
Thanks to \href{mailto:gergeleit@gmd.de}{Martin Gergeleit}\ for his
port of the original SUN ONC RPC library to Windows/NT, and for his
permission to use his port without any royalties involved. Thanks to
\href{mailto:paul.meurer@hit.uib.no}{Paul Meurer}\ for his help fixing
the Windows/NT LISP client code.  Thanks to
\href{mailto:joswig@lispmachine.de}{RainerJoswig}\ for setting up and
maintaining the first \plob\ mailing list (\lisp{plob@lisp.de})
and the WWW \href{http://www.lisp.de}{site}\ hosting the first \plob\ 
archives. \href{mabramso@nlm.nih.gov}{Myriam Abramson}\ pointed out
some bugs, thanks for that.

%%% Local Variables: 
%%% buffer-file-coding-system: iso-latin-1-unix
%%% mode: latex
%%% TeX-master: "userg"
%%% End: 
