%
\begin{deflist}[XXXXXXXXXXXXXXX]

\item[Architecture] Client/server

\item[Operating systems] Solaris 2.x, Linux kernel version 2.x, IRIX
  6.x, Windows/NT 4.0.

\item[LISP systems]
  \href{http://www.harlequin.co.uk/products/ads/lispworks/lispworks.html}{\lwcl}\ 
  3.x for Unix and 4.0.1 for Windows/NT,
  \href{http://www.franz.com/products/products.html}{\allegrocl}\ 4.3
  for Unix and 5.0 beta for Unix and Windows/NT.

\item[Databases per Server] Any number of open databases.

\item[Databases per Client] 1

\item[Multi user access] Multiple clients can connect to one server
  process.

\item[Object space size] Maximum of 384 MB per database (1 GB on a
  Windows/NT server). This is a technical limit of the low-level
  persistent storage used for the server.

\item[Access control] Login deny/allow on per-machine basis

\item[Lock protocol] Hierarchical locking.

\item[Lock levels] Whole storage, object, slot.

\item[Lock modes] Read-only, read, write; read-only intent, read
  intent, write intent

\item[Transactions] Flat transactions. Concurrent transactions are
  supported, both between different clients and between different
  database sessions of a single client.

\item[Access protocol] Two phased transactions and locking of the
  persistent object at object state transfer between client and
  server.

\item[Indexes supported] Btrees on slots of persistent \clos\ 
  instances are maintained automatically; direct usage of btrees is
  possible.

\item[LISP types] All types defined in \cite{bib:CLtLII} are
  supported, with the exception of binary function code.

\item[Name spaces] Persistent packages containing persistent symbols.

\end{deflist}
